On Secure Delegation of SampBQP with a Classical Client

### 2020-02-28 blind.tex
Update SampBQP blindness proof

\def\SampB{\mathsf{Samp, blind}}
\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
\nc{\VSampB}{\ensuremath{V_\SampB}}
\nc{\PSampB}{\ensuremath{P_\SampB}}

@@

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
	\Ethan{too hand-wavy still, can still say ``identically simulates"}
	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
	\Ethan{Soundness def. is different}
\end{prf}

>>>>

\def\SampB{\mathsf{Samp, blind}}
\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
\nc{\VSampB}{\ensuremath{V_\SampB}}
\nc{\PSampB}{\ensuremath{P_\SampB}}
\nc{\PSampBstar}{\ensuremath{P_\SampB^*}}
\nc{\cVSampB}[1]{\ensuremath{\cV_{\SampB,#1}}}
\nc{\cPSampB}[1]{\ensuremath{\cP_{\SampB,#1}}}

@@

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof is almost identical to that of \cref{thm:BlindBQP}.

	The completeness follows by inspection.
	For blindness, the prover receives only $ct_x$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.

	Now we prove the soundness of $\PiSampB$.
	Suppose for the sake of contradiction that there exists some cheating prover $\PSampBstar$ with some acceptance probability $\varepsilon\notin O(\frac{1}{\poly(n)})$.
	Then we can construct a prover $\PSampstar$ violating the soundness guarantees of $\PiSamp$ by simulating $(\VSampB(x), \PSampBstar)$ as below:

	We define $\PSampstar$ to first generate
	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$,
	then runs $\sigma\leftarrow\cPSampB{1}(pk, ct_x)$.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VSamp$ qubit-by-qubit.

	We now prove that $\PSampstar$ in fact violates the soundness of $\PiSamp$.
	Observe that the experiments $(\PSampstar, \VSamp)(x)$ and $(\PSampBstar, \VSampB(x))$ are identical except for how $w$ is obtained from $\sigma$,
	so by \cref{decodeMeasureOrder} they are equivalent.
	Hence we have $\PSampstar$ with acceptance probability $\varepsilon$, which is a contradiction.
\end{prf}
